### 2017-11-06 Elle/Elle-output.tex

\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
    \inferrule* [right={\tiny tenL}] {
      $$\mprset{flushleft}
    \inferrule* [right={\tiny Fl}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny beta}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny tenR}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny ax}] {
                \,
              }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
            }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
            \\
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny ax}] {
                \,
              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
            }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
          }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A >>}}}
        }{\texttt{\textcolor{red}{<<no parses (char 22): x1 : Gf A, y1 : Gf B ;*** . \mbox{$\mid$}- ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0) : h(F Gf B) (x) F Gf A >>}}}
      }{\texttt{\textcolor{red}{<<no parses (char 11): x1 : Gf A ;*** y2 : F Gf B \mbox{$\mid$}- let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)) : h(F Gf B) (x) F Gf A >>}}}
    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x2 : F Gf A, y2 : F Gf B \mbox{$\mid$}- let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0))) : h(F Gf B) (x) F Gf A >>}}}
    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** z : h(F Gf A) (x) F Gf B \mbox{$\mid$}- let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf B) (x) F Gf A) >>}}}
    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** . \mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf A) (x) F Gf B . let z : h(F Gf A) (x) F Gf B be x2 (x) y2 in (let x2 : F Gf A be F x1 in (let y2 : F Gf B be F y1 in (ex y1 , x1 with y0 , x0 in (h(F y0) (x) F x0)))) : (h(F Gf A) (x) F Gf B) -> (h(F Gf B) (x) F Gf A) >>}}}
  \end{math}
\end{center}

Deriving right contraction in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny tenL}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Fl}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny contrR}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny tenR}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny Fr}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny ax}] {
                    \,
                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                }{\texttt{\textcolor{red}{<<no parses (char 10): x1 : Gf A;*** . \mbox{$\mid$}- F x1 : F Gf A >>}}}
                \\
                \inferrule* [right={\tiny tenR}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
                  }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
                  \\
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                  }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
                }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F y0) (x) F x0 : h(F Gf B) (x) F Gf A >>}}}
              }{\texttt{\textcolor{red}{<<no parses (char 33): x1 : Gf A, y0 : Gf B, x0 : Gf A ;*** . \mbox{$\mid$}- h(F x1) (x) (h(F y0) (x) F x0) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
            }{\texttt{\textcolor{red}{<<no parses (char 22): y0 : Gf B, x2 : Gf A ;*** . \mbox{$\mid$}- contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
          }{\texttt{\textcolor{red}{<<no parses (char 11): y0 : Gf B ;*** x3 : F Gf A \mbox{$\mid$}- let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
        }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** y1 : F Gf B, x3 : F Gf A \mbox{$\mid$}- let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0)))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
      }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** z : h(F Gf B) (x) F Gf A \mbox{$\mid$}- let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : h(F Gf A) (x) (h(F Gf B) (x) F Gf A) >>}}}
    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** . \mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf B) (x) F Gf A . let z : h(F Gf B) (x) F Gf A be y1 (x) x3 in (let y1 : F Gf B be F y0 in (let x3 : F Gf A be F x2 in (contrR x2 as x1, x0 in (h(F x1) (x) (h(F y0) (x) F x0))))) : (h(F Gf B) (x) F Gf A) -> (h(F Gf A) (x) (h(F Gf B) (x) F Gf A)) >>}}}
  \end{math}
\end{center}

Deriving left contraction in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny tenL}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Fl}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny contrR}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny tenR}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny tenR}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                  }{\texttt{\textcolor{red}{<<no parses (char 10): x0 : Gf A;*** . \mbox{$\mid$}- F x0 : F Gf A >>}}}
                  \\
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny ax}] {
                      \,
                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
                  }{\texttt{\textcolor{red}{<<no parses (char 10): y0 : Gf B;*** . \mbox{$\mid$}- F y0 : F Gf B >>}}}
                }{\texttt{\textcolor{red}{<<no parses (char 22): x0 : Gf A, y0 : Gf B ;*** . \mbox{$\mid$}- h(F x0) (x) F y0 : h(F Gf A) (x) F Gf B >>}}}
                \\
                \inferrule* [right={\tiny Fr}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny ax}] {
                    \,
                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                }{\texttt{\textcolor{red}{<<no parses (char 10): x1 : Gf A;*** . \mbox{$\mid$}- F x1 : F Gf A >>}}}
              }{\texttt{\textcolor{red}{<<no parses (char 33): x0 : Gf A, y0 : Gf B, x1 : Gf A ;*** . \mbox{$\mid$}- (h(F x0) (x) F y0) (x) F x1 : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
            }{\texttt{\textcolor{red}{<<no parses (char 22): x2 : Gf A, y0 : Gf B ;*** . \mbox{$\mid$}- contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
          }{\texttt{\textcolor{red}{<<no parses (char 11): x2 : Gf A ;*** y1 : F Gf B \mbox{$\mid$}- let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
        }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x3 : F Gf A, y1 : F Gf B \mbox{$\mid$}- let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1))) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
      }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** z : h(F Gf A) (x) F Gf B \mbox{$\mid$}- let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x2 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in ((h(F x0) (x) F y0) (x) F x1)))) : (h(F Gf A) (x) F Gf B) (x) F Gf A >>}}}
    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** . \mbox{$\mid$}- \mbox{$\backslash{}$}l z : h(F Gf A) (x) F Gf B . let z : h(F Gf A) (x) F Gf B be x3 (x) y1 in (let x3 : F Gf A be F x3 in (let y1 : F Gf B be F y0 in (contrL x2 as x0, x1 in (h(F x0) (x) (h(F y0) (x) F x1))))) : (h(F Gf A) (x) F Gf B) -> ((h(F Gf A) (x) F Gf B) (x) F Gf A) >>}}}
  \end{math}
\end{center}

Deriving weakening in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny weak}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny unitR}] {
            \,
          }{\texttt{\textcolor{red}{<<no parses (char 10): . \mbox{$\mid$}- triv ***: Unit >>}}}
        }{\texttt{\textcolor{red}{<<no parses (char 11): x0 : Gf A ;*** . \mbox{$\mid$}- weak x0 in triv : Unit >>}}}
      }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** x1 : F Gf A \mbox{$\mid$}- let x1 : F Gf A be F x0 in weak x0 in triv : Unit >>}}}
    }{\texttt{\textcolor{red}{<<no parses (char 3): . ;*** . \mbox{$\mid$}- \mbox{$\backslash{}$}l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit) >>}}}
  \end{math}
\end{center}

>>>>

    \inferrule* [right={\tiny imprR}] {
              }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{C}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
            \\
              }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
            }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
        }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
      }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
    }{\ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{,}  \ottmv{y_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
    }{\ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \triangleright  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
    }{ \cdot   \vdash_\mathcal{L}   \lambda_r  \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   .  \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\, \ottmv{x_{{\mathrm{2}}}}  \triangleright  \ottmv{y_{{\mathrm{2}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{2}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{1}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{ex}\, \ottmv{y_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{1}}}} \,\mathsf{with}\, \ottmv{y_{{\mathrm{0}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}    \ottsym{:}  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{)}  \rightharpoonup  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}

Deriving right contraction in Elle comonadicly:
    \inferrule* [right={\tiny imprR}] {
            \inferrule* [right={\tiny contrR}] {
                  }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{1}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                \\
                    }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{C}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B} }
                  }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{y_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}  }
                  \\
                    }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{C}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A} }
                  }{\ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}  }
                }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}  }
              }{\ottmv{x_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \ottsym{,}  \ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
            }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{2}}}}  \ottsym{:}   \mathsf{G} \ottnt{A}   \vdash_\mathcal{L}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
          }{\ottmv{y_{{\mathrm{0}}}}  \ottsym{:}   \mathsf{G} \ottnt{B}   \ottsym{,}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
        }{\ottmv{y_{{\mathrm{1}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{B}    \ottsym{,}  \ottmv{x_{{\mathrm{3}}}}  \ottsym{:}   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
      }{\ottmv{z}  \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \vdash_\mathcal{L}   \mathsf{let}\, \ottmv{z}  :    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\, \ottmv{y_{{\mathrm{1}}}}  \triangleright  \ottmv{x_{{\mathrm{3}}}} \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{y_{{\mathrm{1}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{B}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{y_{{\mathrm{0}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{let}\, \ottmv{x_{{\mathrm{3}}}}  :   \mathsf{F}  \mathsf{G} \ottnt{A}   \,\mathsf{be}\,  \mathsf{F}\, \ottmv{x_{{\mathrm{2}}}}  \,\mathsf{in}\, \ottsym{(}   \mathsf{contrR}\, \ottmv{x_{{\mathrm{2}}}} \,\mathsf{as}\, \ottmv{x_{{\mathrm{1}}}} , \ottmv{x_{{\mathrm{0}}}} \,\mathsf{in}\, \ottsym{(}    \mathsf{F} \ottmv{x_{{\mathrm{1}}}}    \triangleright  \ottsym{(}    \mathsf{F} \ottmv{y_{{\mathrm{0}}}}    \triangleright   \mathsf{F} \ottmv{x_{{\mathrm{0}}}}   \ottsym{)}  \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{)}   \ottsym{:}    \mathsf{F}  \mathsf{G} \ottnt{A}     \triangleright  \ottsym{(}    \mathsf{F}  \mathsf{G} \ottnt{B}     \triangleright   \mathsf{F}  \mathsf{G} \ottnt{A}    \ottsym{)}}
